% !TEX encoding = UTF-8 Unicode

\begin{thebibliography}{x}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{artistic}
Papari, Giuseppe, Nicolai Petkov, and Patrizio Campisi. \emph{Artistic edge and corner enhancing smoothing}. IEEE Transactions on Image Processing 16.10 (2007): 2449-2462.

\bibitem{intellipaint}
Reese, L. Jack, and William A. Barrett. \emph{Image editing with intelligent paint}. Proceedings of Eurographics. Vol. 21. No. 3. 2002.

\bibitem{instagram}
Instagram, hivatalos weboldal, \texttt{https://www.instagram.com/}, Internet, 2018.

\bibitem{snapchat}
Snapchat, hivatalos weboldal, \texttt{https://www.snapchat.com/}, Internet, 2018.

\bibitem{messenger}
FaceBook messenger, hivatalos weboldal, \texttt{https://www.messenger.com/features}, Internet, 2018.

\bibitem{prisma}
Prisma, hivatalos weboldal, \texttt{https://prisma-ai.com/}, Internet, 2018.

\bibitem{pixect}
Pixect, hivatalos weboldal, \texttt{https://www.pixect.com/}, Internet, 2018.

\bibitem{jetset}
Smilebit: \emph{Jet Set Radio}, SEGA, \texttt{http://www.sega.com/games/jet-set-radio}, Internet, 2003.

\bibitem{scannerdarkly}
The New York Times, \emph{'A Scanner Darkly': Keanu Reeves, Undercover and Flying High on a Paranoid Head Trip}, 2006. július 7.

\bibitem{czap}
Czap László: Képfeldolgozás, egyetemi jegyzet, Miskolci Egyetem, \\ \texttt{http://mazsola.iit.uni-miskolc.hu/~czap/HEFOP/Kepfeld1010.pdf}, 2007.

\bibitem{kato}
Kató Zoltán: Digitális képfeldolgozás, egyetemi kurzus, Szegedi Tudományegyetem, \texttt{http://www.inf.u-szeged.hu/~kato/teaching/DigitalisKepfeldolgozasTG}, 2014.

\bibitem{bilateral}
Paris, Sylvain, et al. \emph{A gentle introduction to bilateral filtering and its applications}. ACM SIGGRAPH 2007 courses. ACM, 2007.

\bibitem{beyeler} Michael Beyeler: \emph{How to create a cool cartoon effect with OpenCV and Python}, \texttt{http://www.askaswiss.com/2016/01/} \texttt{how-to-create-cartoon-effect-opencv-python.html}, 2016. január 5.

\bibitem{beyeler2} Michael Beyeler: \emph{How to create a beautiful pencil sketch effect with OpenCV and Python}, \texttt{http://www.askaswiss.com/2016/01/} \texttt{how-to-create-pencil-sketch-opencv-python.html}, 2016. január 13.

\bibitem{emami} Shervin Emami: \emph{Mastering OpenCV with Practical Computer Vision Projects}, Packt Publishing, 2012.

\bibitem{opencv}
Bradski, Gary, and Adrian Kaehler. Learning OpenCV: \emph{Computer vision with the OpenCV library}. O'Reilly Media, Inc., 2008.

% TODO: Artistic filter-es könyv.

\end{thebibliography}